---
title: "Day5_stats"
author: "Shale"
date: "8/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Stats practice

## `starwars` dataset

```{r, include=FALSE}
summary(starwars)
head(starwars)
# wtf is up with birth_year?
```

## Graphy stuff
`include=` show/hide code and output
`echo=` show/hide code (output still shown)
`eval=FALSE` prevents the chunk from running

```{r, echo=FALSE, warning=FALSE}
ggplot(data = starwars, aes(x=height, y=mass))+
  geom_point()
```

## simple stats
`na.rm = TRUE` will remove NA values (since `mean` won't evaluate with NAs). 

```{r}
sw_h_mn = mean(starwars$height, na.rm = TRUE)
sw_h_vr = var(starwars$height, na.rm = TRUE)
sw_h_sd = sqrt(sw_h_vr)
# sd(starwars$height, na.rm = TRUE) would also give standard deviation

```

## best practice describing data
Using inline code to present values instead of manual transfer

Mean character height: `r round(sw_h_mn, 1)` cm
Variance in the height of all characters: `r round(sw_h_vr, 1)` cm^2
With a standard deviation of `r round(sw_h_sd, 1)` cm


## Logical / boolean

`|` or
`&` and
`!` not

```{r}
# numberics 
5>10
10 <= 13

#strings
"cat" > "elephant"
"stupid" == "stupid"

# vectors
centipedes <- c(2, 4, 6, 2, 7, 9, 6, 8)
centipedes <= 4
centipedes <=3 | centipedes >= 7
centipedes != 6


# odd stuff
0 == FALSE
1 == TRUE
# both return true (but 0 == TRUE returns FALSE, 1 == FALSE returns FALSE)

```

```{r}

```










